City traffic, IoT and Blockchain technologies

### 2020-11-04 thesis/report2.tex
More and more work on report 2.

    % Privacy aware IOTA ledger: Decentralized mixing and unlinkable IOTA transactions

@@

>>>>

    \cite{PrivacyAwareIOTALedger} tackles another area: privacy or anonimity. Various techinques, the authors are claiming, offers the ability for a Bictoin account, or an IOTA account to be identified and tracked such that two informations can be obtain: total balance and transaction history. They summarize various related works of mixing services where tokens are exchanged, based on fees both for Bitcoin and for IOTA. Then they proceed to define the problem with few design goals: anonimity, correctness, compatibility, no mixing fees and efficiency. Their proposal have three phases. Phase 1 is called settlement and its aim is to take a pledge from the participants. Phase 2 is called outputs shuffling and it randomizes input and output addresses. Thus no participant can learn what relation was originally between any input address and any output address. Phase 3 is called transaction and it assures that the funds are correctly transferred from the inputs to the outputs. This mixiing protocol assures the properties discussed earlier.

@@

    Bitcoin is capable only of a limited, non Turing-complete ability of executing smart contracts. Therefore its main purpose remained transfer of money. Many other blockchain technologies, most notable being Ethereum, has been designed from the ground up to have support for smart contracts. Ethereum has a virtual machine, called Ethereum Virtual Machine (EVM). The EVM takes an input from the current Ethereum state and produces an output or a transaction. It is a stack machine with a depth of 1024 items, where each item is a 256-bit word. Every client implementation has an EVM implementation because each client has to be able to execute smart contracts. EVM have those smart contracts being \say{on-chain}. This means they are part of the core protocol. Execution and validation are being made by all nodes in the protocol. This offers a good security architecture and as much as the network grows it will improve the security even more. Smart contracts, which are one of the two types of Ethereum accounts (the other being the usual user accounts), are able to transfer tokens from their account without providing the usual signature of an user account. But there also disadvantages. All nodes have to execute a smart contracts and this leads to a lack of scalability. Their execution cost money (gas in Ethereum paralance). Thus the second type of smart contracts appear in sight: \say{off-chain}. The main difference is that not all nodes are mandated to execute them and thus the consensus is not part of the core protocol. The advantages are first the scalability because not all the nodes need to take part into the consensus. The greatest disadvantage is the lack of privacy (hence the work of \cite{PrivacyAwareIOTALedger} to improve it).

    What are the roles of smart contracts, though? Ever since the blockchain gained wider adoption the insufficiency of Bitcoin, first one of its kind and still the most successfull, has been an obstacle for implementing other types of transactions than the simple money transfer. Therefore other blockchain have started to be designed from the ground up to allow more complex logic. Examples are plenty: decentralized voting, assets transfer and ownership, etc.
